\LARGE \bf A Pipeline to Assemble (Near-)Collision Footage Datasets

### 2020-11-11 paper.tex
Adding 2 histograms

\pgfplotstableread[col sep=comma]{by-classes.csv}\byclass

@@

>>>>

\pgfplotstableread[col sep=comma]{by-classes.csv}\byclass
\pgfplotstableread[col sep=comma]{by-actors.csv}\byactors
\pgfplotstableread[col sep=comma]{by-duration.csv}\byduration

@@

\begin{figure}[htpb]
		\centering
    \begin{tikzpicture}
    \begin{axis}[
      title={Videos by actors},
      xlabel={Number of actors},
      ylabel={Frequency (\# of videos)},
      xtick=data,
      xticklabels from table={\byactors}{X}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byactors;
    \end{axis}
    \end{tikzpicture}
		\caption{Videos by number of actors}
		\label{fig:vids-by-actors}
\end{figure}

\begin{figure}[htpb]
		\centering
    \begin{tikzpicture}
    \begin{axis}[
      title={Videos by duration},
      xlabel={Duration (in frames)},
      ylabel={Frequency (\# of videos)},
      xtick=data,
      xticklabels from table={\byduration}{X}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byduration;
    \end{axis}
    \end{tikzpicture}
		\caption{Videos by duration}
		\label{fig:vids-by-duration}
\end{figure}
